Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
AWS iniciado

Thanks to the shareability introduced by {rCUDA}, all VM in the cloud 
environment should be able to use and share all the GPUs installed in 
the physical nodes removing the current limitation. But, in order to achieve this goal, 
the cloud facilities need to be provided with the {rCUDA} software and 
in the case of OpenStack, a module for configuring virtualized GPUs 
 has to be implemented.

\begin{itemize}
\item Actual estado de las tecnolog\'ias de cloud
\item Limitaciones que nos llevan a realizar este trabajo
\item Beneficios de la unión de ambas tecnolog\'ias
\end{itemize}

\section{Working with AWS}
\label{sec:aws}

\subsection{Current Features}

\subsubsection{Instances}
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{AWS Instances}
\label{table:awsInstances}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccccc}
Name & vCPUs & Memory & Network & GPUs & Price\\ \hline \hline
c3.2xlarge & 8 & 15 GiB & High & 0 & \$ 0.21\\ \hline
c3.8xlarge & 32 & 60 GiB & 10 Gb & 0 & \$ 1.68 \\ \hline
g2.2xlarge & 8 & 15 GiB & High & 1 & \$ 0.65\\ \hline
g2.8xlarge & 32 & 60 GiB & 10 Gb & 4 & \$ 2.6 \\ \hline
\end{tabular}\end{center}\end{table}

\subsubsection{Network}
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{IPERF results between instances}
\label{table:iperf}
\tabcolsep=0.24cm
\begin{center}\begin{tabular}{cccc}
Server & Client & Network & BandWidth\\ \hline \hline
g2.8xlarge & c3.2xlarge & High & 1  Gb/s\\ \hline
g2.8xlarge & c3.8xlarge & 10Gb & 7.5  Gb/s\\ \hline
g2.8xlarge & g2.2xlarge & High & 1 Gb/s\\ \hline
g2.8xlarge & g2.8xlarge & 10Gb & 7.5  Gb/s\\ \hline
\end{tabular}\end{center}\end{table}

@@

\begin{figure*}[ht]
\centering
\subfigure[5 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws3.png}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws2.png}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws1.png}
\label{subfig:aws3}}
\caption{An AWS instance with several remote GPUs}
\label{fig:aws}
\end{figure*}

\subsection{Testbed Scenarios}
\subsection{Experiments}
\subsection{Results}
Flexibility and economical expenses

>>>>

Thanks to the shareability introduced by {rCUDA}, all VM in the cloud 
environment should be able to use and share all the GPUs installed in 
the physical nodes removing the current limitation. But, in order to achieve this goal, 
the cloud facilities need to be provided with the {rCUDA} software and 
in the case of OpenStack, a module for manageing virtualized GPUs 
 has to be implemented.

\section{Working with AWS}
\label{sec:aws}
In this section, first of all, the current user-level features 
provided by the Amazon Web Services are explained and analyzed 
from the point of view of the GPU usage. 
Finally, the scenarios and experiments where virtualized GPUs are utilized are 
described and first results are showed.

\subsection{Current Features}
This subsection explains the most common features checked during 
the virtual machine creation step.

\subsubsection{Instances}

An instance is a pre-configured virtual machine focused on an 
specific target. Inside the large list of instances offered by AWS, 
we can find: general pourpose (T2, M4 and M3); computer science optimized 
(C4 and C3); memory optimized (R3); storage optimized (I2 and D2) and 
GPU capable instances. Each kind of instance has its own pourpose and its 
own price. Moreover, each instance has different number of CPUs and network 
interconnection which can be: low, medium, high or 10Gb.

For this study, the instances presented in the Table~\ref{table:awsInstances} 
have been selected. The C3 family instances, which are not equipped with 
GPUs are going to be used as client whereas the instances of the G2 family are 
acting as servers.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{AWS Instances}
\label{table:awsInstances}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccccc}
Name & vCPUs & Memory & Network & GPUs & Price\\ \hline \hline
c3.2xlarge & 8 & 15 GiB & High & 0 & \$ 0.21\\ \hline
c3.8xlarge & 32 & 60 GiB & 10 Gb & 0 & \$ 1.68 \\ \hline
g2.2xlarge & 8 & 15 GiB & High & 1 & \$ 0.65\\ \hline
g2.8xlarge & 32 & 60 GiB & 10 Gb & 4 & \$ 2.6 \\ \hline
\end{tabular}\end{center}\end{table}

\subsubsection{Network behaviour}
As it is shown in the Table~\ref{table:awsInstances}, each instance has different 
interconnection and taking into account that the use of the network 
is critical when GPU virtualization is applied, a simple test to verify the 
real network bandwidth is needed.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{IPERF results between instances}
\label{table:iperf}
\tabcolsep=0.24cm
\begin{center}\begin{tabular}{cccc}
Server & Client & Network & BandWidth\\ \hline \hline
g2.8xlarge & c3.2xlarge & High & 1  Gb/s\\ \hline
g2.8xlarge & c3.8xlarge & 10Gb & 7.5  Gb/s\\ \hline
g2.8xlarge & g2.2xlarge & High & 1 Gb/s\\ \hline
g2.8xlarge & g2.8xlarge & 10Gb & 7.5  Gb/s\\ \hline
\end{tabular}\end{center}\end{table}

The IPERF tool has been executed between the instances showed in 
the Table~\ref{table:iperf} in order to know the real bandwidth.
Therefore, we can assure that the nomenclature ''High'' used in the 
network column correspond to a 1Gb interconnection and the 10Gb has 
a real bandwidth of 7.5Gb/s.

@@

\subsection{Testbed Scenarios}
\begin{figure*}[ht]
\centering
\subfigure[5 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws3.png}
\label{subfig:aws1}}
\quad
\subfigure[8 remote GPUs over 10GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws2.png}
\label{subfig:aws2}}
\subfigure[13 remote GPUs over 1GbE]{%
\includegraphics[width=0.31\linewidth]{images/aws1.png}
\label{subfig:aws3}}
\caption{An AWS instance with several remote GPUs}
\label{fig:aws}
\end{figure*}

\subsection{Experiments}
\subsection{Results}
Flexibility and economical expenses
